# Datasets

```{r setup, include=FALSE, warning=FALSE, message=FALSE,out.width="120%"}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)



```

```{r global, cache.comments=FALSE,comment=FALSE,warning=FALSE,message=FALSE}

library(sf)
library(dplyr)
library(readxl)
library(flextable)
library(magrittr)
library(ggplot2)
library(plotly)
admin0_aoi<-st_read("o_nap_countries/admin0_aoi.shp")
towns<-st_read("o_nap_countries/towns_aoi.shp")
basin1<-st_read("o_nap_countries/basins1_aoi.shp")
basin2<-st_read("o_nap_countries/basins2_aoi.shp")
basin3<-st_read("o_nap_countries/basins3_aoi.shp")
basin5<-st_read( "C:\\Users\\Makabe\\opennaps\\HydroAtlas\\o_nap_countries\\basins5_aoi.shp")
basin8<-st_read( "C:\\Users\\Makabe\\opennaps\\HydroAtlas\\o_nap_countries\\basins8_aoi.shp")
riv<-st_read( "C:\\Users\\Makabe\\opennaps\\HydroAtlas\\o_nap_countries\\rivers_aoi.shp")
riv_bigdis<-riv%>%filter(riv$dis_m3_pyr>10)
riv_bigclas<-riv%>%filter(riv$ORD_CLAS<3)
capitals<-towns<-filter(towns, towns$featurecla=="Admin-0 capital")


```


```{r,eval=FALSE}
#plot(admin0_aoi$geometry,bg = "#ffffff")
plot(basin8[, basin8$glc_cl_smj],
     breaks = "fisher",
     nbreaks = 5,
     border=NA,
     pal = hcl.colors(5),
     main = "Natural Discharge \n (m³/yr)",legend=T)
#plot(riv$geometry,lwd=1/riv$ORD_CLAS*2,col='blue', add=TRUE)


```

## Natural Discharge {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,1)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
t1<-set_caption(t1, "Natural Discharge ")

t1

```

```{r }

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff", color=NA,size=0.5, lty=2) +
 
  geom_sf(data = riv_bigdis, lwd=0, mapping=aes(fill= riv_bigdis$dis_m3_pyr)) +
  geom_sf(data = riv_bigdis, fill= riv_bigdis$dis_m3_pyr, color=riv_bigdis$dis_m3_pyr) +
  scale_fill_viridis_c(name=paste('m³/year'))+
  geom_sf(data= basin3, lty=1, lwd=0.85, fill=NA)+
  geom_sf(data = capitals, color="grey40") +
  #geom_sf_label(data = capitals, aes(label=name),size=2.4, position = "identity")+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Natural Discharge")

```

## Land Surface Runoff {-}

```{r}
library(readxl)
library(flextable)
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,2)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Land Surface Runoff ")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, lwd=0, mapping=aes(fill=run_mm_syr),color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('mm/yr'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40", size=4,pch=20, alpha=0.9, show.legend = T) +
  #geom_sf_label(data = capitals, aes(label=name),size=1.8)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Land Surface Runoff")
  #theme(legend.position = 'bottom', legend.title = element_text('mm/yr'))

```

## Inundation Extent {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,3)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Inundation Extent ")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=inu_pc_slt), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Inundation extent'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Inundation Extent")

```

## Limnicity (Percent Lake Area) {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,4)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Limnicity (Percent Lake Area) ")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=lka_pc_sse*0.1), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Limnicity (Percent Lake Area)")

```

## Lake Volume {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,5)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Lake Volume ")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=lkv_mc_usu*0.001), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Upstream Total \n million m³'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Lake Volume")

```

## Reservoir Volume {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,6)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Reservoir Volume ")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=rev_mc_usu), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Upstream Total \n million m³'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Reservoir Volume")

```

## Degree of Regulation {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,7)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Degree of Regulation ")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  #geom_sf(data = basin5, aes(fill=dor_pc_pva), color=NA) +
  #scale_fill_viridis_c(direction = -1, name=paste('DOR \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis, color=riv_bigdis$dis_m3_pyr) +
  #scale_fill_viridis_c(name=paste('DOR \n %'))+
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  ggtitle("Degree of Regulation")

```

## River Area {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,8)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "River Area ")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=ria_ha_ssu), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n hectares'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("River Area")

```

## River Volume {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,9)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "River Volume ")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=riv_tc_ssu*0.001), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Total Volume \n \'000 m³'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("River Volume")

```

## Groundwater Table Depth {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,10)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Groundwater Table Depth ")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=gwt_cm_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average Depth \n cm'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Groundwater Table Depth")

```

## Elevation {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,11)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Elevation ")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=ele_mt_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average Elevation \n m a.s.l'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Elevation")

```

## Terrain Slope {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,12)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Terrain Slope ")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=basin5$slp_dg_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average Slope \n degrees'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Terrain Slope")

```

## Stream Gradient {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,13)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Stream Gradient ")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=sgr_dk_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average Gradient \n decimeters per km'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Stream Gradient")

```

## Climate Zones {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,14)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Climate Zones ")

t1

```


```{r}
ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  
  geom_sf(data = basin8, aes(fill=clz_cl_smj), color=NA) +
  scale_fill_gradientn(breaks=c(7,9,11,12,13,14,15,17,18), 
                       labels=c("Cold and mesic","Cool temperate and xeric", "Warm temperate and mesic","Warm temperate and xeric", "Hot and mesic", "Hot and dry", "Hot and arid","Extremely hot and xeric", "Extremely hot and moist"), 
                       colours = c("#007248","#38a700", "#98e500", "#d0ff73", "#faf5f0","#efdfcd","#d9af82","#e67b24", "#7d4204"
                                   ),limits=c(6.8,18.5),  
                 space = "Lab",name=paste("Classes"),na.value = NA, guide = 'colourbar', aesthetics = 'fill', n.breaks=10)+
 
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  #geom_sf(data = riv_bigdis, color='#8282FF') +
  geom_sf(data = capitals, fill="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text", x=31, y=-34.5, label = "_____ Basin boundary", color="grey40")+
  ggtitle("Climate Zones")+
  theme(legend.key.size = unit(0.8, 'cm'),legend.title = element_text(size=10),legend.text = element_text(size=7),legend.position = c(1.24, .24), legend.background = element_blank())

```


## Climate Strata {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,15)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Climate Strata ")

t1

```


```{r }

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=cls_cl_smj), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste(''))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.6, bgcolor='none')+
  geom_sf_text(data = basin5, aes(label=cls_cl_smj),size=3, check_overlap = T)+
  ggtitle("Climate Strata")+
  #annotate("text", x=34, y=-34.5, label = "*Check table[clz.cl]for classes")+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+

  theme(legend.position = 'none')

```



## Air Temperature {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,16)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Air Temperature")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=tmp_dc_syr), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Annual Average \n °C'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Air Temperature")

```


## Precipitation {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,17)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Precipitation")

t1

```


```{r}


ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=basin5$pre_mm_syr), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Annual Average \n mm'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Precipitation")

```

## Potential Evapotranspiration {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,18)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Potential Evapotranspiration")

t1

```


```{r}


ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=pet_mm_syr), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Annual Average \n mm'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Potential Evapotranspiration")

```

## Actual Evapotranspiration {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,19)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Actual Evapotranspiration")

t1

```


```{r}


ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=aet_mm_syr), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Annual Average \n mm'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Actual Evapotranspiration")

```

## Global Aridity Index {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,20)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Global Aridity Index")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=basin5$ari_ix_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average AI \n value'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Global Aridity Index")

```

## Climate Moisture Index  {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,21)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Climate Moisture Index")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=cmi_ix_syr), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Annual Average \n index value'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Climate Moisture Index")

```

## Snow Cover Extent {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,22)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Snow Cover Extent")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=snw_pc_syr), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Annual Average \n % cover'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Snow Cover Extent")

```

## Land cover Classes {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,23)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Land cover Classes")

t1

```

```{r }
ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  
  geom_sf(data = basin8, aes(fill=glc_cl_smj), color=NA) +
  scale_fill_gradientn(breaks=c(20,18.5, 16, 14,12.5, 11,8, 6, 4,2), 
                       labels=c("Water Body","Bare Area", "Cultivated and managed land", "Herbaceous cover, sparse", "Herbaceous cover, closed-open", "Shrub cover, closed-open", "Tree cover, regulary flooded", "Tree cover, mixed leaf type","Tree cover, needle-leaved","Tree cover, broad-leaved"), 
                       colours = c("#267300", "#72a700", "#6fa701","#89cd63","#c4f26f","#a9a800",
                                   "#cbcc64",  "#f678b5", "#ffe9bb","#005be7"),limits=c(1,20),  
                 space = "Lab",name=paste("Land Cover"),na.value = NA, guide = 'colourbar', aesthetics = 'fill', n.breaks=10)+
 
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  #geom_sf(data = riv_bigdis, color='#8282FF') +
  geom_sf(data = capitals, fill="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Land Cover Classes")+
  theme(legend.key.size = unit(0.8, 'cm'),legend.title = element_text(size=10),legend.text = element_text(size=7),legend.position = c(1.24, .24), legend.background = element_blank())


```

 
## Land Cover Extent {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,24)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Land Cover Extent")

t1

```

```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=glc_pc_s01), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Land Cover Extent: Tree cover, broadleaved, evergreen")

```

## Potential Natural Vegetation Classes {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,25)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Potential Natural Vegetation Classes")

t1

```


```{r }
ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  
  geom_sf(data = basin8, aes(fill=pnv_cl_smj), color=NA) +
  scale_fill_gradientn(breaks=c(1,2,3,9,10,11,12,14), 
                       labels=c("Tropical evergreen forest","Tropical deciduous forest", "Temperate broadleaf \nevergreen forest", "Savanna", "Grassland/steppe", "Dense shrubland", "Open shrubland", "Desert"), 
                       colours = c("#267300", "#72a700", "#6fa701","#89cd63","#c4f26f","#a9a800",
                                   "#cbcc64",  "#f678b5"),limits=c(0,14),  
                 space = "Lab",name=paste("Classes"),na.value = NA, guide = 'colourbar', aesthetics = 'fill', n.breaks=10)+
 
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  #geom_sf(data = riv_bigdis, color='#8282FF') +
  geom_sf(data = capitals, fill="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text", x=30, y=-34, label = "_____ Basin boundary", color="grey40")+
  ggtitle("Potential Natural Vegetation Classes")+
  theme(legend.key.size = unit(0.8, 'cm'),legend.title = element_text(size=10),legend.text = element_text(size=7),legend.position = c(1.24, .24), legend.background = element_blank())



```


## Potential Natural vegetation Extent {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,26)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Potential Natural vegetation Extent:Tropical Evergreen ")

t1

```


```{r}

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=pnv_pc_s01), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Potential Natural Vegtation Extent: Tropical Evergreen")

```

## Wetland Classes {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,27)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Wetland Classes")

t1

```

```{r }
ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  
  geom_sf(data = basin8, aes(fill=wet_cl_smj), color=NA) +
  scale_fill_gradientn(breaks=c(1,2,3,4,6,7,9), 
                       labels=c("Lake","Reservoir", "River", "Freshwater marsh, floodplain", "Coastal wetland \n(incl. mangove, estuary, \ndelta, lagoon)", "Pan, brackish/saline wetland", "Intermittent wetland/lake"), 
                       colours = c("#002573", "#e60000", "#7e00a4","#0167eb","#fca57b","#fffa06",
                                   "71defd"),limits=c(1,9),  
                 space = "Lab",name=paste("Classes"),na.value = 'grey', guide = 'colourbar', aesthetics = 'fill', n.breaks=10)+
 
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  #geom_sf(data = riv_bigdis, color='#8282FF') +
  geom_sf(data = capitals, fill="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text", x=34, y=-33, label = "_____ Basin boundary", color="grey40")+
  ggtitle("Wetland Classes")+
  annotate("text", x=34, y=-34.5, label = "*Grey area=No values")+
 theme(legend.key.size = unit(0.8, 'cm'),legend.title = element_text(size=10),legend.text = element_text(size=8),legend.position = c(1.20, .24), legend.background = element_blank())


```



## Wetland Extent {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,28)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Wetland Extent")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=wet_pc_s01), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  ggtitle("Wetland Extent: Class 01")

```

## Forest Cover Extent {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,29)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Forest Cover Extent ")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=for_pc_sse), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Forest Cover Extent")

```

## Cropland Extent {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,30)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Cropland Extent")

t1

```


```{r}


ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=crp_pc_sse), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Cropland Extent")

```

## Pasture Extent {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,31)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Pasture Extent")

t1

```


```{r}


ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=pst_pc_sse), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Pasture Extent")

```

## Irrigated Area Extent (Equipped) {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,32)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Irrigated Area Extent (Equipped)")

t1

```


```{r}


ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=crp_pc_sse), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Irrigated Area Extent (Equipped)")

```

## Glacier Extent {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,33)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Glacier Extent")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=gla_pc_sse), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Glacier Extent")

```

## Permafrost Extent {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,34)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Permafrost Extent ")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=prm_pc_sse), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Permafrost Extent")

```

## Protected Area Extent {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,35)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Protected Area Extent ")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=pac_pc_sse), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Protected Area Extent")

```

## Terrestrial Biomes {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,36)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Terrestrial Biomes")

t1

```

```{r }
ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  
  geom_sf(data = basin8, aes(fill=tbi_cl_smj), color=NA) +
  scale_fill_gradientn(breaks=c(1,7,10,12,13), 
                       labels=c("Tropical & Subtropical \nMoist Broadleaf Forests","Tropical & Subtropical \nGrasslands, Savannas & \nShrublands", "Montane Grasslands &\n Shrublands", "Mediterranean Forests, \nWoodlands & Scrub", "Deserts & Xeric Shrublands"), 
                       colours = c("#267300", "#72a700", "#6fa701","#89cd63","#c4f26f"),limits=c(0,13),  
                 space = "Lab",name=paste("Classes"),na.value = NA, guide = 'colourbar', aesthetics = 'fill', n.breaks=10)+
 
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  #geom_sf(data = riv_bigdis, color='#8282FF') +
  geom_sf(data = capitals, fill="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Terrestrial Biomes")
 theme(legend.key.size = unit(0.8, 'cm'),legend.title = element_text(size=10),legend.text = element_text(size=8),legend.position = c(1.20, .24), legend.background = element_blank())


```


## Terrestrial Ecoregions {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,37)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Terrestrial Ecoregions")

t1

```


```{r }

#scale_fill_gradientn(colours = terrain.colors(10),limits=c(0,100),  
                 #space = "Lab",name=paste("Inundation Extent /%"),na.value = NA)

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=tec_cl_smj), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  #geom_line(aes(x=35, y=-35), label="Basin boundary")+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.6, bgcolor='none')+
  geom_sf_text(data = basin5, aes(label=tec_cl_smj),size=3, check_overlap = T)+
  ggtitle("Terrestrial Ecoregions")+
  annotate("text", x=34, y=-34.5, label = "*Check table for classes")+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+

  theme(legend.position = 'none')

```

* Check table [tec_cl] for class names

## Freshwater Major Habitat Types {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,38)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Freshwater Major Habitat Types")

t1

```


```{r }
ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  
  geom_sf(data = basin5, aes(fill=fmh_cl_smj), color=NA) +
  scale_fill_gradientn(breaks=c(1.2,3,4,5,6,8,9,10.1), 
                       labels=c("LargeLakes","Montane freshwaters", "Xeric freshwaters \nand endorheic basins", "Temperate coastal rivers", "Temperate upland rivers", "Tropical and subtropical \ncoastal rivers", "Tropical and subtropical \nupland rivers","Tropical and subtropical \nfloodplain rivers \nand wetlands"), 
                       colours = c("#02c5ff", "#a63800", "#f4c97a","#004da7","#a83c7a","#38a700",
                                   "276300","#779c33"),limits=c(0.8,10.2),  
                 space = "Lab",name=paste("Classes"),na.value = 'grey', guide = 'colourbar', aesthetics = 'fill', n.breaks=10)+
 
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  #geom_sf(data = riv_bigdis, color='#8282FF') +
  geom_sf(data = capitals, fill="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Freshwater Major Habitat Types")+
theme(legend.key.size = unit(0.8, 'cm'),legend.title = element_text(size=10),legend.text = element_text(size=8),legend.position = c(1.20, .24), legend.background = element_blank())


```


## Freshwater Ecoregions {-}
```{r}

attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,39)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Freshwater Ecoregions")

t1

```

```{r }

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=fec_cl_smj), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste(''))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.6, bgcolor='none')+
  geom_sf_text(data = basin5, aes(label=fec_cl_smj),size=3, check_overlap = T)+
  ggtitle("Freshwater Ecoregions")+
  annotate("text", x=34, y=-34.5, label = "*Check table for classes")+
  annotate("text", x=34, y=-33, label = "_____ Basin boundary", color="grey40")+

  theme(legend.position = 'none')

```


* Check table [fec_cl] for class names 


## Clay Fraction in Soil {-}
```{r}

attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,40)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Clay Fraction in Soil")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=cly_pc_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average \nfraction in\n top 5cm \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Clay Fraction in Soil")

```

## Silt Fraction in Soil {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,41)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Silt Fraction in Soil")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=slt_pc_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average \nfraction in \ntop 5cm \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Silt Fraction in Soil")

```

## Sand Fraction in Soil {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,42)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Sand Fraction in Soil")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=snd_pc_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average \nfraction in \ntop 5cm \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Sand Fraction in Soil")

```

## Organic Carbon Content in Soil {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,43)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Organic Carbon Content in Soil")

t1

```


```{r}


ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=soc_th_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average carbon \nstock in top 5cm \n tonnes/hectare'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Organic Carbon Content in Soil")

```

## Soil Water Content {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,44)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Soil Water Content")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=snw_pc_syr), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average \nwater content \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Soil Water Content")

```

## Lithological Classes {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,45)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Lithological Classes")

t1

```

```{r }
ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  
  geom_sf(data = basin8, aes(fill=lit_cl_smj), color=NA) +
  scale_fill_gradientn(breaks=c(1,3,6,8,9,10,11), 
                       labels=c("Unconsolidated Sediments (SU)","Siliciclastic Sedimentary Rocks (SS)", "Carbonate Sedimentary Rocks (SC)", "Metamorphic Rocks (MT)", "Acid Plutonic Rocks (PA)", "Intermediate Volcanic Rocks (VI)", "Water Bodies (WB)"), 
                       colours = c("#7473c8", "#458970", "#4d0074","#014c73","#6777ce","#71004d",
                                   "03c2ff"),limits=c(0,11),  
                 space = "Lab",name=paste("Classes"),na.value = 'grey', guide = 'colourbar', aesthetics = 'fill', n.breaks=10)+
 
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  #geom_sf(data = riv_bigdis, color='#8282FF') +
  geom_sf(data = capitals, fill="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Lithological Classes")+
   theme(legend.key.size = unit(0.8, 'cm'),legend.title = element_text(size=10),legend.text = element_text(size=7),legend.position = c(1.24, .24), legend.background = element_blank())


```



## Karst Area Extent {-}
```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,46)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Karst Area Extent")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=kar_pc_sse), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste(' '))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Karst Area Extent")

```

## Soil Erosion {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,47)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Soil Erosion")

t1

```


```{r}


ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=ero_kh_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average rate \n kg/hectare/year'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Soil Erosion")

```

## Population Count {-}

```{r}
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,48)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Population Count")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=pop_ct_ssu), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Total population \n number of people'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Population Count")

```

## Population Density {-}

```{r}

attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,49)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Population Density")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=ppd_pk_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Population density \n people/km²'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Population Density")

```

## Urban Extent {-}

```{r}

attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,50)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Urban Extent ")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=urb_pc_sse), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Spatial Extent \n %'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Urban Extent")

```

## Nighttime Lights {-}

```{r}

attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,51)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Nighttime Lights ")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=nli_ix_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average radiance \n digital number'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Nighttime Lights")

```

## Road Density {-}

```{r}

attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,52)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Road Density")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=rdd_mk_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average density \n meters/km²'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Road Density")

```

## Human Footprint {-}

```{r}

attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,53)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Human Footprint")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=hft_ix_s09), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average footprint \nindex value'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Human Foootprint:2009")

```

## Global Admnistrative Areas {-}

```{r}

attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,54)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Global Admnistrative Areas")

t1

```

```{r }

ggplot() + 
  
  geom_sf(data = basin5, aes(fill=gad_id_smj), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste(''))+
  #geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  #geom_sf(data = riv_bigdis,fill="#4fffff") +
  #geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4, bgcolor='none')+
  #geom_sf_text(data = basin5, aes(label=gad_id_smj),size=3, check_overlap = T)+
  #geom_sf(data = admin0_aoi, fill=NA, color='gray') +
  ggtitle("Global Admnistrative Areas")+
  annotate("text", x=16, y=-12, label = "Angola")+
  annotate("text", x=24, y=-20, label = "Botswana")+
  annotate("text", x=16, y=-22, label = "Namibia")+
  annotate("text", x=31.5, y=-26.5, label = "Lesotho")+
  annotate("text", x=33.4, y=-13, label = "Malawi")+
  annotate("text", x=35, y=-18, label = "Mozambique")+
  annotate("text", x=23, y=-30, label = "South Africa")+
  annotate("text", x=28.4, y=-29.6, label = "Eswatini")+
  annotate("text", x=25, y=-14, label = "Zambia")+
  annotate("text", x=30, y=-20, label = "Zimbabwe")+
  theme(legend.position = 'none')

```


## Gross Domestic Product {-}

```{r}
library(readxl)
library(flextable)
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,55)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Gross Domestic Product")

t1

```


```{r}


ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=gdp_ud_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average GDP\n per capita \n us $'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Gross Domestic Product")

```

## Human Development Index {-}

```{r}
library(readxl)
library(flextable)
attributes<-read_excel("attributes.xlsx", sheet = 'attributes')
att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
att_df$V0<-rownames(att_df)


t1<-flextable(att_df[,c(57,56)])
t1<-delete_part(t1, part = 'header') 
t1<-width(t1,j=2, width = 25, unit = "in")
t1<-bold(t1,i=3)
t1<-bold(t1, j=1)
t1<-hline(t1, part="all" )
#t1<-vline(t1, j=1 )
#t1<-set_caption(t1, "Human Development Index")

t1

```


```{r}

ggplot() + 
  #geom_sf(data = admin0_aoi, fill="#ffffff") +
  geom_sf(data = basin5, aes(fill=hdi_ix_sav), color=NA) +
  scale_fill_viridis_c(direction = -1, name=paste('Average HDI \nindex value'))+
  geom_sf(data= basin3, fill=NA, alpha=0.5, lty=1, lwd=0.85)+
  geom_sf(data = riv_bigdis,fill="#4fffff") +
  geom_sf(data = capitals, color="grey40") +
  geom_sf_label(data = capitals, aes(label=name),size=2.4)+
  annotate("text",x=34, y=-33,label = "_____ Basin boundary", color="grey40")+
  ggtitle("Human Development Index")

```