# HydroATLAS_v10_Legends

## HydroATLAS v1.0 Legends {-}
```{r, echo=F}
library(readxl)
library(flextable)
leg.attr<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'HydroATLAS v1.0 Legends')
#att_df<-as.data.frame(t(attributes[,-c(5,6,7)]))
#att_df$V0<-rownames(att_df)

t1<-flextable(leg.attr,col_keys = names(leg.attr),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```

## Climate Zones (clz.cl) {-}
```{r, echo=F}
library(readxl)
clz.cl<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'clz_cl')

t1<-flextable(clz.cl,col_keys = names(clz.cl),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```

## Climate Strata (cls.cl) {-}
```{r, echo=F}
library(readxl)
cls.cl<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'cls_cl')

t1<-flextable(cls.cl,col_keys = names(cls.cl),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```

## Land cover classes (glc.cl) {-}
```{r, echo=F}
library(readxl)
glc.cl<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'glc_cl')

t1<-flextable(glc.cl,col_keys = names(glc.cl),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```

## Potential Natural Vegetation Classes (pnv.cl) {-}
```{r, echo=F}
library(readxl)
pnv.cl<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'pnv_cl')

t1<-flextable(pnv.cl,col_keys = names(pnv.cl),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```

## Wetland Classes (wet.cl) {-}
```{r, echo=F}
library(readxl)
wet.cl<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'wet_cl')

t1<-flextable(wet.cl,col_keys = names(wet.cl),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```

## Terrestrial Biomes (tbi.cl) {-}
```{r, echo=F}
library(readxl)
tbi.cl<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'tbi_cl')

t1<-flextable(tbi.cl,col_keys = names(tbi.cl),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```

## Terrestrial Ecoregions (tec.cl) {-}
```{r, echo=F}
library(readxl)
tec.cl<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'tec_cl')

t1<-flextable(tec.cl,col_keys = names(tec.cl),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```

## "Freshwater Major Habitat Types (fmh.cl) {-}
```{r, echo=F}
library(readxl)
fmh.cl<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'fmh_cl')

t1<-flextable(fmh.cl,col_keys = names(fmh.cl),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```

## Freshwater Ecoregions (fec.cl) {-}
```{r, echo=F}
library(readxl)
fec.cl<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'fec_cl')

t1<-flextable(fec.cl,col_keys = names(fec.cl),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```

## Lithological Classes (lit.cl) {-}
```{r, echo=F}
library(readxl)
lit.cl<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'lit_cl')

t1<-flextable(lit.cl,col_keys = names(lit.cl),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```

## Global Admnistrative Areas( gad.id) {-}
```{r, echo=F}
library(readxl)
gad.id<-read_excel("HydroATLAS_v10_Legends.xlsx", sheet = 'gad_id')

t1<-flextable(gad.id,col_keys = names(gad.id),
  cwidth = 3,
  cheight = 0.01,
  defaults = list(),
   theme_booktabs())
t1<-fontsize(t1,part = 'all', size = 8)
t1<-border_outer(t1,part = 'all', border = NULL)
t1<-border_inner(t1,part = 'all', border = NULL)
t1<-bold(t1, part = 'header')
t1

```



